Cross-Validation Default

### 2024-10-09 docsrc/documentation/notebooks/mental_well_being.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

```{r SF12_Density}
continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
```

@@

```{r SF12_Output, echo=FALSE}
options(width=120)
ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
```

>>>>

```{r SF12_Density}
continuous_density("data/transitions/SF_12_MCS/OLS/SF_12_MCS_2018_2019.rds", "next_SF_12_MCS")  
```

@@

```{r SF12_Output, echo=FALSE}
options(width=120)
ols_output("data/transitions/SF_12_MCS/OLS/SF_12_MCS_2018_2019.rds")
ols_histogram("data/transitions/SF_12_MCS/OLS/SF_12_MCS_2018_2019.rds", "next_SF_12_MCS")
```

### 2024-10-09 minos/outcomes/spatial_analysis_gbis.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

continuous_var_table$`EPCG Variable Mean` <- epcg_continuous_table$Variable.Mean
continuous_var_table <- continuous_var_table[, c("Variable", "LSOA Type", "EPCG Variable Mean", "GBIS Variable Mean")]

print(xtable(discrete_var_table, type = "latex"), file = here::here("plots", "GBIS_discrete_var_table.tex"))
print(xtable(continuous_var_table, type = "latex"), file = here::here("plots", "GBIS_continuous_var_table.tex"))

>>>>

continuous_var_table$`EPCG Variable Mean` <- epcg_continuous_table$Variable.Mean
continuous_var_table <- continuous_var_table[, c("Variable", "LSOA Type", "EPCG Variable Mean", "GBIS Variable Mean")]
continuous_var_table <- continuous_var_table[, c("Variable", "LSOA Type", "GBIS Variable Mean", "EPCG Variable Mean")]

print(xtable(discrete_var_table, type = "latex"), file = here::here("plots", "GBIS_discrete_var_table.tex"), include.rownames=FALSE)
print(xtable(continuous_var_table, type = "latex"), file = here::here("plots", "GBIS_continuous_var_table.tex"), include.rownames=FALSE)

### 2024-10-09 minos/outcomes/standard_deviation_change_SF12.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

```{r}
# Calculate difference in SF12 between individuals in both scenarios for every year
base.subset <- base %>% 
  select(pidp, time, SF_12) %>%
  rename(SF12.base = SF_12)
int.subset <- int %>% 
  select(pidp, time, income_boosted, SF_12) %>%
  rename(SF12.int = SF_12,
         boosted = income_boosted)

@@

```{r}
# get just one year
#b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
b.2030 <- base %>% filter(time == 2030, SF_12 != -8.0)
i.2030 <- int %>% filter(time == 2030, SF_12 != -8.0)
```

```{r}
# get just the SF12 columns
b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
#b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
```

>>>>

```{r}
# Calculate difference in SF12 between individuals in both scenarios for every year
base.subset <- base %>% 
  select(pidp, time, SF_12_MCS) %>%
  rename(SF12.base = SF_12_MCS)
int.subset <- int %>% 
  select(pidp, time, income_boosted, SF_12_MCS) %>%
  rename(SF12.int = SF_12_MCS,
         boosted = income_boosted)

@@

```{r}
# get just one year
#b.2020 <- base %>% filter(time == 2020, SF_12_MCS != -8.0)
b.2030 <- base %>% filter(time == 2030, SF_12_MCS != -8.0)
i.2030 <- int %>% filter(time == 2030, SF_12_MCS != -8.0)
```

```{r}
# get just the SF12 columns
b.2030 <- b.2030 %>% select(pidp, SF_12_MCS) %>% rename(baseline = SF_12_MCS)
i.2030 <- i.2030 %>% select(pidp, SF_12_MCS) %>% rename(intervention = SF_12_MCS)
#b.2020 <- b.2020 %>% select(pidp, SF_12_MCS) %>% rename(initial = SF_12_MCS)
#b.2030 <- b.2030 %>% select(pidp, SF_12_MCS) %>% rename(end = SF_12_MCS)
#i.2030 <- i.2030 %>% select(pidp, SF_12_MCS) %>% rename(end = SF_12_MCS)
```

### 2024-10-09 minos/testing/rate_of_change_testing.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

SF_12.stats <- diff_by_whole_period_quintile(raw.dat, 'SF_12')
```

@@

## SF_12_MCS

Quick look at SF_12_MCS also.

```{r}
spaghetti_plot(old.dat, 'SF_12')
spaghetti_plot(new.dat, 'SF_12')
spaghetti_plot(raw.dat, 'SF_12')
```

@@

```{r}
violin_plot(old.dat, 'SF_12')
violin_plot(new.dat, 'SF_12')
violin_plot(raw.dat, 'SF_12')
```

@@

## MODELS
mod.path <- 'Minos/data/transitions/cross_validation/'
sf12.mod <- readRDS(paste0(mod.path, 'SF_12/ols2/SF_12_2017_2018.rds'))
income.mod <- readRDS(paste0(mod.path, 'hh_income/ols2/hh_income_2019_2020.rds'))

@@

```{r}
#miss.values <- c(-9, -8, -7, -3, -2, -1, -10)
#raw <- raw.cv %>%
#  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
#  group_by(pidp) %>%
#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
#         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
#  filter(time != 2009)

#base <- base.cv %>%
#  filter(!hh_income %in% miss.values, !SF_12 %in% miss.values) %>%
#  group_by(pidp) %>%
#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
#         diff.SF12_MCS = SF_12 - lag(SF_12, order_by = time)) %>%
#  filter(time != 2014)
```

@@

```{r}
#test <- base.cv %>%
#  group_by(time) %>%
#  summarise(mean.income = mean(hh_income, na.rm = TRUE),
#            mean.SF12 = mean(SF_12, na.rm = TRUE))

>>>>

SF_12_MCS.stats <- diff_by_whole_period_quintile(raw.dat, 'SF_12_MCS')
```

@@

## SF_12_MCS_MCS

Quick look at SF_12_MCS_MCS also.

```{r}
spaghetti_plot(old.dat, 'SF_12_MCS')
spaghetti_plot(new.dat, 'SF_12_MCS')
spaghetti_plot(raw.dat, 'SF_12_MCS')
```

@@

```{r}
violin_plot(old.dat, 'SF_12_MCS')
violin_plot(new.dat, 'SF_12_MCS')
violin_plot(raw.dat, 'SF_12_MCS')
```

@@

## MODELS
mod.path <- 'Minos/data/transitions/cross_validation/'
sf12.mod <- readRDS(paste0(mod.path, 'SF_12_MCS/ols2/SF_12_MCS_2017_2018.rds'))
income.mod <- readRDS(paste0(mod.path, 'hh_income/ols2/hh_income_2019_2020.rds'))

@@

```{r}
#miss.values <- c(-9, -8, -7, -3, -2, -1, -10)
#raw <- raw.cv %>%
#  filter(!hh_income %in% miss.values, !SF_12_MCS %in% miss.values) %>%
#  group_by(pidp) %>%
#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
#         diff.SF12_MCS = SF_12_MCS - lag(SF_12_MCS, order_by = time)) %>%
#  filter(time != 2009)

#base <- base.cv %>%
#  filter(!hh_income %in% miss.values, !SF_12_MCS %in% miss.values) %>%
#  group_by(pidp) %>%
#  mutate(diff.hh_income = hh_income - lag(hh_income, order_by = time),
#         diff.SF12_MCS = SF_12_MCS - lag(SF_12_MCS, order_by = time)) %>%
#  filter(time != 2014)
```

@@

```{r}
#test <- base.cv %>%
#  group_by(time) %>%
#  summarise(mean.income = mean(hh_income, na.rm = TRUE),
#            mean.SF12 = mean(SF_12_MCS, na.rm = TRUE))

### 2024-10-09 minos/validation/DEBUG.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

### SF12
```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.sf12.2 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

```{r}
sf12 <- data %>% 
  select(pidp, time, SF_12)

# calculate and plot mean over time
sf12.byyr <- data %>% group_by(time) %>%
  summarise(SF_12 = mean(SF_12))

ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12)) +
  geom_line()
```

@@

ggplot(data = sf12.joined, mapping = aes(x = SF_12, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

@@

```{r}
print("2018:")
sprintf("Min: %f", min(sf12.2018$SF_12))
sprintf("Max: %f", max(sf12.2018$SF_12))
sprintf("Mean: %f", mean(sf12.2018$SF_12))
print("2020:")
sprintf("Min: %f", min(sf12.2020$SF_12))
sprintf("Max: %f", max(sf12.2020$SF_12))
sprintf("Mean: %f", mean(sf12.2020$SF_12))
print("2030:")
sprintf("Min: %f", min(sf12.2030$SF_12))
sprintf("Max: %f", max(sf12.2030$SF_12))
sprintf("Mean: %f", mean(sf12.2030$SF_12))
```

@@

educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
```

@@

```{r}
f.sf12 <- raw.dat %>% select(pidp, time, SF_12)
c.sf12 <- correct %>% select(pidp, time, SF_12)

@@

Now see if any SF_12 values are missing in either the final data or corrected.

```{r}
sum(is.na(f.sf12$SF_12))
sum(is.na(c.sf12$SF_12))

sum(f.sf12$SF_12 == -9)
sum(c.sf12$SF_12 == -9)

@@

# missing by year
final.miss <- f.drop %>% 
  group_by(time) %>%
  summarise(final.missing = sum((SF_12 == -9)))

correct.miss <- c.drop %>% 
  group_by(time) %>%
  summarise(correct.missing = sum((SF_12 == -9)))

>>>>

### SF12
```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.sf12.2 <- raw.dat %>% 
  select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

```{r}
sf12 <- data %>% 
  select(pidp, time, SF_12_MCS)

# calculate and plot mean over time
sf12.byyr <- data %>% group_by(time) %>%
  summarise(SF_12_MCS = mean(SF_12_MCS))

ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12_MCS)) +
  geom_line()
```

@@

ggplot(data = sf12.joined, mapping = aes(x = SF_12_MCS, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

@@

```{r}
print("2018:")
sprintf("Min: %f", min(sf12.2018$SF_12_MCS))
sprintf("Max: %f", max(sf12.2018$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2018$SF_12_MCS))
print("2020:")
sprintf("Min: %f", min(sf12.2020$SF_12_MCS))
sprintf("Max: %f", max(sf12.2020$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2020$SF_12_MCS))
print("2030:")
sprintf("Min: %f", min(sf12.2030$SF_12_MCS))
sprintf("Max: %f", max(sf12.2030$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2030$SF_12_MCS))
```

@@

educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
sf_12.mod <- readRDS(paste0(trans.path, 'SF_12_MCS/ols/SF_12_MCS_2018_2019.rds'))
house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
```

@@

```{r}
f.sf12 <- raw.dat %>% select(pidp, time, SF_12_MCS)
c.sf12 <- correct %>% select(pidp, time, SF_12_MCS)

@@

Now see if any SF_12_MCS values are missing in either the final data or corrected.

```{r}
sum(is.na(f.sf12$SF_12_MCS))
sum(is.na(c.sf12$SF_12_MCS))

sum(f.sf12$SF_12_MCS == -9)
sum(c.sf12$SF_12_MCS == -9)

@@

# missing by year
final.miss <- f.drop %>% 
  group_by(time) %>%
  summarise(final.missing = sum((SF_12_MCS == -9)))

correct.miss <- c.drop %>% 
  group_by(time) %>%
  summarise(correct.missing = sum((SF_12_MCS == -9)))

### 2024-10-09 minos/validation/cross_validation_default.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

# SF_12

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12')
multi_year_boxplots(raw, cv, 'SF_12')
snapshot_OP_plots(raw, cv, 'SF_12', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```

>>>>

# SF_12_MCS

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'SF_12_MCS')
multi_year_boxplots(raw, cv, 'SF_12_MCS')
snapshot_OP_plots(raw, cv, 'SF_12_MCS', target.years = c(2015, 2017, 2019, 2021))
q_q_comparison(raw, cv, 'SF_12_MCS')
```
```{r}
sf12.14 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2015)
print(sf12.14)
```
```{r}
sf12.16 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2017)
print(sf12.16)
```
```{r}
sf12.18 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2019)
print(sf12.18)
```
```{r}
sf12.20 <- marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'SF_12_MCS', 
                                 target.year = 2021)
print(sf12.20)
rm(sf12.14, sf12.16, sf12.18, sf12.20)
```
